Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-12 paper/paper.tex
fixed some bugs

	\begin{table}[htb]
		\tiny
		\centering
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
			\hline
			\begin{tabular}{c}
				\textbf{model}\\
				\hline
				{SVM}\\
				{1D CNN\cite{hu2015deep}}\\
				{2D CNN\cite{liu2017semi}}\\
				{3D CNN\cite{hamida20183}}\\
				{3D FCN\cite{lee2016contextual}}\\
				{CNN-MRF\cite{cao2018hyperspectral}}\\
				{CapsNet}\\
				{DCCN}\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}&
			\begin{tabular}{ccc}
				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
				\hline
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
				100\%&100\%&100\%\\
			\end{tabular}\\
			\hline
		\end{tabular}
		\caption{Final result of all adopted models.}
		\label{result}
	\end{table}

>>>>

	\begin{table}[htb]
		\tiny
		\centering
		\resizebox{\textwidth}{!}{
			\begin{tabular}{c|c|c|c|c}
				\hline
				no item&\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
				\hline
				\begin{tabular}{c}
					\textbf{metrics}\\
					\hline
					{SVM}\\
					{2D CNN\cite{liu2017semi}}\\
					{3D CNN\cite{hamida20183}}\\
					{3D CNN-MS\cite{he2017multi}}\\
					{3D FCN\cite{lee2016contextual}}\\
					{CNN-MRF\cite{cao2018hyperspectral}}\\
					{CapsNet}\\
					{DCCN}\\
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					97.52±0.07 & 91.74±0.33 & 96.49±0.10\\%{SVM}\\
					98.27±0.14 & 97.24±0.54 & 97.56±0.19\\%{2D CNN\cite{liu2017semi}}\\
					95.25±2.99 & 89.74±7.37 & 93.32±4.21\\%{3D CNN\cite{hamida20183}}\\
					98.03±0.40 & 96.31±1.42 & 97.22±0.56\\%{3D CNN\cite{he2017multi}}\\
					98.33±0.59 & 94.65±2.09 & 97.64±0.83\\%{3D FCN\cite{lee2016contextual}}\\
					99.24±0.23 & 97.54±1.04 & 98.92±0.33\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
					99.48±0.09 & 98.50±0.21 & 99.27±0.12\\%{CapsNet}\\
					\textbf{99.53±0.02} & \textbf{98.59±0.20} & \textbf{99.34±0.03}\\%{DCCN}\\
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					79.86±0.26 & 64.26±0.45 & 71.86±0.39\\%{SVM}\\
					93.74±0.42 & 95.61±0.79 & 91.85±0.54\\%{2D CNN\cite{liu2017semi}}\\
					77.92±12.22 & 85.34±7.42 & 73.42±13.63\\%{3D CNN\cite{hamida20183}}\\
					93.39±1.34 & 95.97±1.39 & 91.42±1.72\\%{3D CNN\cite{he2017multi}}\\
					88.45±1.66 & 85.58±3.22 & 84.49±2.22\\%{3D FCN\cite{lee2016contextual}}\\
					98.07±0.62 & 96.80±1.06 & 97.44±0.82\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
					97.69±0.60 & 96.82±0.83 & 96.94±0.80\\%{DCCN}\\
					\textbf{98.40±0.19} & \textbf{97.77±0.33} & \textbf{97.89±0.25}\\%{CapsNet}\\
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					82.45±0.75 & 86.16±0.93 & 80.24±0.87\\%{SVM}\\
					92.24±1.19 & 95.82±0.61 & 91.36±1.34\\%{2D CNN\cite{liu2017semi}}\\
					88.27±4.18 & 92.76±2.96 & 86.87±4.74\\%{3D CNN\cite{hamida20183}}\\
					91.29±2.91 & 95.08±1.68 & 90.28±3.27\\%{3D CNN\cite{he2017multi}}\\
					87.11±3.77 & 90.10±3.66 & 85.57±4.28\\%{3D FCN\cite{lee2016contextual}}\\
					94.69±1.48 & 97.39±0.80 & 94.07±1.66\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
					94.48±0.59 & 96.84±0.58 & 93.83±0.66\\%{DCCN}\\
					\textbf{95.00±0.59} & \textbf{97.30±0.50} & \textbf{94.42±0.66}\\%{CapsNet}\\
				\end{tabular}&
				\begin{tabular}{ccc}
					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
					\hline
					97.44±0.19 & 97.42±0.22 & 96.80±0.23\\%{SVM}\\
					84.47±0.51 & 89.86±0.69 & 81.22±0.62\\%{2D CNN\cite{liu2017semi}}\\
					79.27±4.74 & 80.81±8.80 & 74.70±5.96\\%{3D CNN\cite{hamida20183}}\\
					79.92±4.91 & 85.46±5.01 & 75.99±5.69\\%{3D CNN\cite{he2017multi}}\\
					86.54±3.72 & 85.55±4.30 & 83.09±4.65\\%{3D FCN\cite{lee2016contextual}}\\
					98.00±1.61 & 97.10±2.33 & 97.48±2.03\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
					99.52±0.10 & 99.31±0.15 & 99.40±0.13\\%{CapsNet}\\
					\textbf{99.56±0.05} & \textbf{99.36±0.07} & \textbf{99.45±0.06}\\%{DCCN}\\
				\end{tabular}\\
			\end{tabular}
		}
	\end{table}
